Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-03-12 analysis/paper.Rmd
adding description and license

---
title: "Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation"
author: "Team Fresh"
date: "2/24/2020"
output: word_document
---

>>>>

---
title: "Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation"
author: "Corey Christopherson, Zachary Garcia, Richard Todd, Thomas Winegarden"
date: "2/24/2020"
output: word_document
---
